Periodograms for Multiband Astronomical Time Series

### 2015-05-12 writeup/paper.tex
add note on floating-mean model

As an example of one of these generalizations, we'll consider \old{what Zechmeister \& Kurster (2009) call the ``generalized Lomb-Scargle method'', and which we'll call the floating-mean periodogram.}
\new{what has variously been called the {\it Date-compensated periodogram} \citep{Ferraz-Mello81}, the {\it floating-mean periodogram} \citep{Cumming99}, and the {\it generalized Lomb-Scargle method} \citep{Zechmeister09}. Here we use the term {\it floating-mean periodogram}.} This method adjusts the classic normalized periodogram by fitting the mean of the model alongside the amplitudes:
\begin{equation}
  y(t~|~\omega, \theta) = \theta_0 + \theta_1\sin\omega t + \theta_2\cos\omega t
\end{equation}
This model can be more accurate than the standard periodogram for certain observing cadences and selection functions. \citet{Zechmeister09} detail the required modifications to the \new{orthogonalized} harmonic formalism of \eq{LombScargle} to allow the mean to float in the model. In the matrix formalism, the modification is much more straightforward: all that is required is to add a column of ones to the $X_\omega$ matrix before computing the power via \eq{LombScargle2}. This column of ones corresponds to a third entry in the parameter vector $\theta$, and acts as a uniform constant offset for all data points.

>>>>

As an example of one of these generalizations, we'll consider \old{what Zechmeister \& Kurster (2009) call the ``generalized Lomb-Scargle method'', and which we'll call the floating-mean periodogram.}
\new{what has variously been called the {\it Date-compensated periodogram} \citep{Ferraz-Mello81}, the {\it floating-mean periodogram} \citep{Cumming99}, and the {\it generalized Lomb-Scargle method} \citep{Zechmeister09}. Here we use the term {\it floating-mean periodogram}.} This method adjusts the classic normalized periodogram by fitting the mean of the model alongside the amplitudes:
\begin{equation}
  y(t~|~\omega, \theta) = \theta_0 + \theta_1\sin\omega t + \theta_2\cos\omega t
\end{equation}
\old{This model} \new{The periodogram derived from this model} can be more accurate than the standard periodogram for certain observing cadences and selection functions. \citet{Zechmeister09} detail the required modifications to the \new{orthogonalized} harmonic formalism of \eq{LombScargle} to allow the mean to float in the model. In the matrix formalism, the modification is much more straightforward: all that is required is to add a column of ones to the $X_\omega$ matrix before computing the power via \eq{LombScargle2}. This column of ones corresponds to a third entry in the parameter vector $\theta$, and acts as a uniform constant offset for all data points.
